\documentclass{article}
\usepackage[top=0.5in, bottom=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\thispagestyle{empty}
 
\begin{document}
	
	\noindent \large \textbf{Edlee Ducay\\}
	\normalsize \small \href{https://github.com/EdleeDucay}{github.com/edleeducay}\hfill Phone: (587) 597-8440 \\
	\normalsize \small \href{https://edleeducay.com/}{edleeducay.com}\hfill Email: \href{mailto:ducay@ualberta.ca}{ducay@ualberta.ca}

\vspace{1mm}
% EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent\textbf{Experience}
\vspace{1mm}
\hrule
\vspace{1mm}
\hfill\break
\noindent  \textbf{Software Developer 1} - \textit{Haemonetics Canada Ltd} \hfill May 2022 - Present
\begin{itemize}[noitemsep, nolistsep]
	\item {Developing, testing and implementing features for a blood transfusion management system called SafeTrace Tx.}
	\item {Migrated automated testing library to playwright increasing efficiency and reducing average runtime by 4\% by enabling testing in parallel.}
	\item {Fixed critical bugs reducing overall instances by 7\% and increasing patient safety.}
	\item {Collaboration with cross-functional teams using agile methodologies, participated in 100\% of daily scrums.}
\end{itemize}
\vspace{1mm}
\noindent  \textbf{Program Facilitator} - \textit{Code Ninjas West Springs} \hfill May 2021 - Aug 2021
\begin{itemize}[noitemsep, nolistsep]
	\item {Tutored students in JavaScript, Python, Lua, HTML, CSS and Scratch.}
	\item {Taught programming in robotics, 3D modeling and game development.}
	\item {Organized and ran hackathons, summer camps and other special events.}
	\item {Introduced and wrote new and creative curriculum relative to computer science.}
\end{itemize}
\vspace{2mm}
% SKILLS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{Skills}
\vspace{1mm}
\hrule
\vspace{1mm}
\hfill\break
	\noindent {Programming Languages:} JavaScript/Typescript, C\#, HTML, CSS, Python, Java, C, Lua, Batch, Latex. \\
	\noindent {Libraries and Frameworks:} Angular, ASP.NET, React, Express, Bootstrap, Django, Flask, Phaser.\\
	\noindent {Tools and Platforms:} Jira, Unix, Windows, AWS, Heroku, Firebase, Docker, GoDaddy, Adobe Photoshop and Premiere. \\
	\noindent {Databases:} SQL Server, Oracle, PostgresSQL, MySQL, SQLite, Firestore.
\vspace{2mm}
\hfill\break
% PROJECTS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf{Projects}
\vspace{1mm}
\hrule
\vspace{1mm}
\hfill\break
% Custom Youtube Playlists
 \textbf {Custom Youtube Playlists} \hfill Aug 2022 - Present \\
\textit {Stack: React, HTML, CSS, Firebase, Youtube API}
\begin{itemize}[noitemsep, nolistsep]
	\item {Currently developing a web application that allows the user to create playlists and customize them.}
	\item {Signin and Signup developed with Firebase Authentication and Firestore for the database.}
	\item {Utilizes the Youtube Data API to handle video search requests.}
\end{itemize}

% Converse and Cook
\noindent \textbf {Converse and Cook} \hfill Sep 2021 - Dec 2021 \\
\textit {Stack: React, Django, MySQL, Google API with OAuth 2.0}
\begin{itemize}[noitemsep, nolistsep]
	\item {Developed an application for a client that required a recipe and receipt management system for their events as a team of five.}
	\item {Recipes are open to the public requiring no authorization and acts as a grocery shopping list with check marking and the convert-units JavaScript library to enable on the go unit conversion.}
	\item{Authorized use is for adding recipes to the database as well ass sending receipts to the admins for reimbursement.}
	\item {Visit Website:
	\href{http://app.conversecook.com}{app.conversecook.com}
	}
\end{itemize}

% Fitness App
\noindent \textbf {Fitness App} \hfill Sep 2021 \\
\textit {Stack: Django, Python, HTML, CSS, SQLite}
\begin{itemize}[noitemsep, nolistsep]
	\item {Developed for daily rep and set tracking for workouts.}
	\item {Stores weight per lift, current time as well as calculates calories burned per session.}
	\item {Collaborated as a team of five for a university held hackathon.}
\end{itemize}

% Baby Names
\noindent \textbf {Baby Names Web App} \hfill Jan 2021 \\
\textit {Stack: Flask, Python, JavaScript, HTML, CSS}
\begin{itemize}[noitemsep, nolistsep]
	\item {Performs a selection of actions to query a database of names of babies born in Alberta from 1980 to 2017.}
	\item {Deployed on heroku: \href{https://baby-names-webapp.herokuapp.com/}{baby-names-webapp.herokuapp.com}}
\end{itemize}
% Book Tracker 
\noindent \textbf {Book Tracker} \hfill Sep 2020 - Dec 2020\\
\textit {Stack: Java, Firebase, Google Maps API}
\begin{itemize}[noitemsep, nolistsep]
	\item {Java based android application for tracking book sharing developed as a team of 6.}
	\item {Implements Firebase Firestore to mark books as loaned, pending, requested and available.}
	\item {Uses the Google Maps API to create a meet up location for loaning.}
\end{itemize}
\hfill\break
% EDUCATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent \textbf {Education}
\vspace{1mm}
\hrule
\vspace{1mm}
\hfill\break
\textbf {University of Alberta | Edmonton, AB} \hfill Graduating April 2024\\
Bachelor of Science: Major in Computing Science and Minor in Mathematics
\vspace{2mm}
\hfill\break
% Hackathons %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent\textbf{Hackathons}
\vspace{1mm}
\hrule
\vspace{1mm}
\begin{itemize}
	\item {HackED 2021}
	\item {CMPUT 401 Hackathon 2021}
	\item {Code Ninjas Canadian Hackathon 2021 (facilitator)}
	\item {Hack the Northeast 2020}
	\item {Hack the North 2020}
\end{itemize}

\end{document}